Approximation as Differentiation

### 2025-07-03 main/first-order.tex
Remove duplicate definition of Galois connection.

The category $\LatGal$ of bounded lattices and Galois connections is semi-additive.

\begin{definition}[Galois connection]
A \emph{Galois connection} $f \adj g: X \to Y$ is a pair of monotone functions $f: Y \to X$ and $g: X \to Y$
between posets satisfying $y \leq g(x) \iff f(y) \leq x$.
\end{definition}

\noindent A Galois connection $f \adj g: X \to Y$ is an adjunction between poset categories, regarding
monotone $f$ and $g$ as functors; $f$ is usually referred to as the \emph{upper} (right) adjoint and $g$ as
the \emph{lower} (left) adjoint. Galois connections are closed under component-wise composition and identities
$\id_X \adj \id_X$.

>>>>

Galois connections (\defref{galois-connection} above) are closed under component-wise composition and
identities. The category $\LatGal$ of bounded lattices and Galois connections is semi-additive.
